### 2020-12-03 old/arxiv_full_version/proof_same_cov.tex

	For equation \eqref{eq_gA_p2}, 
	%using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that all moments of $\varepsilon_i$ exist by Assumption \eqref{assmAhigh2}, 
	using Corollary \ref{cor_calE}, we obtain the following with high probability:
	\begin{align}
		|\inner{XB^{\star} (U_AU_A^{\top} - \id_{t\times t})}{\cE}| &\le n^\e \cdot \sigma \cdot \bignormFro{XB^{\star} (U_AU_A^{\top} - \id_{t\times t})} \nonumber \\
		&\le n^{\e} \cdot \sigma \cdot \norm{Z} \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \nonumber \\
		&\lesssim n^{\e + 1/2} \cdot \sigma \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \label{eq_gA_err2}
%		&\le  n^{c_\infty +c} \cdot \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
	\end{align}
	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
	In the third step, we use Fact \ref{fact_minv}(ii) to bound the operator norm of $Z$ by $\OO(\sqrt{n})$.
	By the AM-GM inequality, equation \eqref{eq_gA_err2} is bounded by the right-hand side of \eqref{eq_gA_err}.

@@

	\bigskip
	Next, we use equation \eqref{eq_gA_err} to prove the claim.
	Using triangle inequality, we upper bound the gap between $h(A^{\star})$ and $h(\hat{A})$:  
	\begin{align}
		h(\hat{A})- h(A^{\star})   &\le \bigabs{g(A^{\star}) - h(A^{\star})} + (g(\hat A) - g({A}^{\star})) + \big|g(\hat{A}) - h(\hat{A})\big| \nonumber \\
		&\le \bigabs{g(A^{\star}) - h(A^{\star})}  + \big|g(\hat{A}) - h(\hat{A})\big|\nonumber \\
		&\lesssim n^{-c_\varphi}\cdot n \bignormFro{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 \cdot n \cdot t. \label{eq_g_gap}
	\end{align}
	The second step used the fact that $\hat A$ is the global minimizer of $g(\cdot)$, so that $g(\hat A) \le g({A}^\star)$.
	The third step used equation \eqref{eq_gA_err} and the fact that the spectral norm of $U_A U_A^{\top} - \id_{t\times t}$ is at most one. 
	%With \eqref{eq_g_gap}, we can derive an upper bound on $\bignormFro{A^{\star} {A^{\star}}^{\top}- U_{\hat{A}} U_{\hat{A}}^{\top}}$ as follows. 
	Using equation \eqref{same_hA}, we can verify that
	$$h(\hat A)-h(A^\star) = n \bigtr{{B^\star}^\top\Sigma B^\star ( A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A})} .$$
	Let $\lambda_1\ge\lambda_2 \ge \cdots\ge \lambda_t$ be the eigenvalues of ${B^\star}^\top\Sigma B^\star$.
	Let $v_i$ be the corresponding eigenvector of $\lambda_i$.
	Then, we have $A^\star {A^\star}^\top =\sum_{i=1}^r v_i v_i^\top$, and
	\begin{align}
	h(\hat A)-h(A^\star) = n \sum_{i=1}^r \lambda_i - n\sum_{i=1}^t \lambda_i \| U^\top_{\hat A} v_i\|^2 &= n\sum_{i=1}^r \lambda_i\left(1 -  \| U^\top_{\hat A} v_i\|^2\right)-n\sum_{i=r+1}^t \lambda_i \| U^\top_{\hat A} v_i\|^2 \nonumber\\
	&\ge  n(\lambda_r-\lambda_{r+1}) \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2 , \label{bdd_A-A}
	\end{align}
	where we use $\sum_{i=1}^r \left(1 -  \| U^\top_{\hat A} v_i\|^2\right) = r- \sum_{i=1}^r  \| U^\top_{\hat A} v_i\|^2 =\sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2  $ in the last step.
	On the other hand, we have
	\begin{align*}
	\| A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A}\|_F^2
	&= 2r - 2\inner{A^{\star}{A^{\star}}^{\top}}{U_{\hat{A}} {U_{\hat{A}}}^{\top}} \\
	&= 2 \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2.
	\end{align*}
	Thus from equation \eqref{eq_g_gap} and  \eqref{bdd_A-A}, we obtain that
	$$\| A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A}\|_F^2  =2 \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2 \lesssim \frac{n^{-c_\varphi}\cdot  \bignormFro{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 t}{\lambda_r- \lambda_{r+1}}  .$$
	Hence the proof is complete.
	\end{proof}

@@

	\paragraph{Part 2:} The second part is the cross term, whose expectation over $\cE$ is zero.
	Let $b = B^{\star} \hat{a}_i - \beta^{(i)}$ for simplicity.
	Using Corollary \ref{cor_calE}, the concentration error can be bounded as
	\begin{align*}
		\bigabs{\inner{\Sigma^{1/2}b}{\Sigma^{1/2}R_i}}
		&= \bigabs{\inner{X (X^{\top}X)^{-1} \Sigma b \hat{a}_i^{\top}}{\cE}} \\
		&\le \sum_{j=1}^t \abs{\hat{a}_i(j)} \cdot \bigabs{\inner{X (X^{\top} X)^{-1} \Sigma b}{\varepsilon^{(j)}}} \\
		&\le \sum_{j=1}^t \abs{\hat{a}_i(j)} \cdot n^{\e}\sigma \bignorm{X (X^{\top}X)^{-1} \Sigma b} \\
		&\le \sqrt{t} \norm{\hat{a}_i} \cdot n^{\e} \sigma \bignorm{X (X^{\top} X)^{-1} \Sigma b}.
	\end{align*}
%	\begin{align*}
%		\bigabs{\inner{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)}{\Sigma^{1/2}R_i}} &= \bigabs{\inner{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)}{\cal E}} \\
%		&\le n^{c}\sigma \cdot \bignormFro{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)}\\
%		&\le n^{c}\sigma \cdot\|\hat a_i\| \cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\| \cdot \| (Z^\top Z)^{-1} \|^{1/2} \\
%		&\lesssim n^{-1/2+c}\sigma \cdot\|\hat a_i\| \cdot \bignorm{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)} \\
%		&\le n^{-1/2+c}\sigma^2  \cdot\|\hat a_i\|^2 + n^{-1/2+c} L(B^{\star} \hat{a}_i), 
%	\end{align*}
	In the first step, we plug in the definition of $R_i$ and re-arrange terms.
	In the second step, we use $\hat{a}_i(j)$ to denote the $j$-th coordinate of $\hat{a}_i$.
	In the third step, we use equation \eqref{vcalE}.
	In the last step, we use $\sum_j |\hat a_i(j)|\le \sqrt{t}\|\hat a_i\|$ by Cauchy-Schwarz inequality.
	Finally, we have
	\begin{align*}
		\bignormFro{ X(X^\top X)^{-1}\Sigma b} &=\left[ {b}^\top \Sigma (X^\top X)^{-1}X^\top X(X^\top X)^{-1}\Sigma b \right]^{1/2} \\
		&\le  \|\Sigma^{1/2} b \|  \cdot \left\| \Sigma^{1/2}(X^\top X)^{-1}\Sigma ^{1/2} \right\|^{1/2}  =   \|\Sigma^{1/2} b \|  \cdot \left\| (Z^\top Z)^{-1}\right\|^{1/2} \\
		&\le n^{-1/2} \cdot \norm{\Sigma^{1/2} b}.
	\end{align*}
%	\begin{align*}
%	\bignormFro{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)} &=\|\hat a_i\|\cdot \left[ (B^{\star} \hat{a}_i - \beta_i)^\top \Sigma (X^\top X)^{-1}X^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i) \right]^{1/2} \\
%	&\le \|\hat a_i\|\cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\|  \cdot \left\| \Sigma^{1/2}(X^\top X)^{-1}\Sigma ^{1/2} \right\|^{1/2} \\
%	&= \|\hat a_i\|\cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\|  \cdot \left\| (Z^\top Z)^{-1}\right\|^{1/2}
%	\end{align*}
	Above, we use $X=Z\Sigma^{1/2}$. In the last step, we use Fact \ref{fact_minv}(ii) to bound the operator norm of $Z^\top Z$ by $\OO(n^{-1})$. %, and apply the AM-GM inequality.
	One can see that the concentration error from this part is upper bounded by the result in Claim \ref{claim_pred_err}.

@@

	\paragraph{Part 3:} The final part is the squared term of $R_i$. We rewrite it as
	\begin{align}
	\|\Sigma^{1/2}R_i\|^2 &= \left\|\sum_{j=1}^t \hat{a}_i(j) \Sigma^{1/2}(X^{\top} X)^{-1} X^{\top} \epsilon^{(j)}\right\|^2 \nonumber\\
	& = \sum_{1\le j , k \le t}\hat a_i(j) \hat a_i(k)  {\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} {\epsilon^{(k)}}.\label{E_i^2}
	\end{align}	
%	If $j\ne k$, using Corollary \ref{cor_calE} we obtain that 
%	\begin{align}
%	\left|{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} {\epsilon^{(k)}} \right| &\le \sigma^2 \cdot \bignormFro{X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} } \nonumber\\
%	& =\sigma^2 \cdot \bignormFro{\Sigma^{1/2}(X^{\top} X)^{-1}\Sigma^{1/2}} \nonumber\\
%	&  \le \sigma^2 \cdot p^{1/2} \cdot \bignorm{(Z^{\top} Z)^{-1}} \lesssim \sigma^2 \cdot n^{-1/2+c} \label{jnek}
%	\end{align}
%	with high probability for any small constant $c>0$. On the other hand, if $j=k$, 
	First, for any $1 \le j, k \le t$, the expectation is
	$$\exarg{\cal E}{{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} \epsilon^{(k)}}=\delta_{jk}\cdot \sigma^2\tr\left[\Sigma(X^\top X)^{-1}\right] .$$
	Second, using equation \eqref{vcalA2}, the concentration error is at most
	\begin{align}
	& \left|{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} {\epsilon^{(k)}} -\delta_{jk}\cdot \sigma^2\tr\left[\Sigma(X^\top X)^{-1}\right]\right|\nonumber \\
	\le &n^c\cdot \sigma^2  \bignormFro{X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} }   = n^c\cdot \sigma^2  \bignormFro{\Sigma^{1/2}(X^{\top} X)^{-1}\Sigma^{1/2}} \nonumber\\
	  \le &\sigma^2 \cdot p^{1/2} \cdot  \bignorm{(Z^{\top} Z)^{-1}}^{1/2} \lesssim \sigma^2 \cdot n^{-1/2+c}. \label{jeqk}
	\end{align}
	Above, we used Fact \ref{fact_minv}(ii) in the last step to bound the operator norm of $(Z^{\top} Z)^{-1}$.
	Plugging equation \eqref{jeqk} into equation \eqref{E_i^2}, we obtain that 
	\begin{align*}
		\bigabs{\bignorm{\Sigma^{1/2} R_i}^2 -  \sigma^2 \|\hat a_i\|^2 \cdot\tr\left[\Sigma(X^\top X)^{-1}\right]} \lesssim  \sigma^2 \cdot n^{-1/2+c}  \sum_{1\le j,k\le t}|\hat a_i(j)||\hat a_i(k)| =  n^{-1/2+c} \sigma^2 \cdot  \|\hat a_i\|^2.
	\end{align*}
%	One can verify that the expectation of $\norm{\Sigma^{1/2} E_i}^2$ is equal to $\sigma^2 \norm{\hat{a}_i}^2 \cdot \tr[\Sigma (X^{\top} X)^{-1}]$.
%	Next, we bound the concentration error.
%	Let $A = X (X^{\top} X)^{-1} \Sigma (X^{\top} X)^{-1} X^{\top}$.
%	We have that
%	\begin{align*}
%		\bigabs{\bignorm{\Sigma^{1/2} E_i}^2 - \exarg{\cE}{\bignorm{\Sigma^{1/2} E_i}^2}}
%		&= \bigabs{\inner{A}{\cE \hat{a}_i \hat{a}_i^{\top} \cE^{\top} - \exarg{\cE}{\cE \hat{a}_i \hat{a}_i^{\top} \cE}}}.
%	\end{align*}
%	In the above equation, we note that the trace of $A$ is precisely the trace of $\Sigma (X^{\top} X)^{-1}$.
%	On the other hand, the concentration error of the spectral norm of $\cE \hat{a}_i \hat{a}_i^{\top} \cE^{\top}$ is at most $\sigma^2 \e $.

>>>>

	For equation \eqref{eq_gA_p2}, 
	%using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that all moments of $\varepsilon_i$ exist by Assumption \eqref{assmAhigh2}, 
	using Corollary \ref{cor_calE}, we obtain the following with high probability:
	\begin{align}
		|\inner{XB^{\star} (U_AU_A^{\top} - \id_{t\times t})}{\cE}| &\le n^\e \cdot \sigma \cdot \bignormFro{XB^{\star} (U_AU_A^{\top} - \id_{t\times t})} \nonumber \\
		&\le n^{\e} \cdot \sigma \cdot \norm{Z} \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \nonumber \\
		&\lesssim n^{\e + 1/2} \cdot \sigma \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} . \label{eq_gA_err2}
%		&\le  n^{c_\infty +c} \cdot \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
	\end{align}
	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
	In the third step, we use Fact \ref{fact_minv}(ii) to bound the operator norm of $Z$ by $\OO(\sqrt{n})$.
	By the AM-GM inequality, equation \eqref{eq_gA_err2} is bounded by the right-hand side of \eqref{eq_gA_err}.

@@

	\medskip
	Next, we use equation \eqref{eq_gA_err} to prove the claim.
	Using triangle inequality, we upper bound the gap between $h(A^{\star})$ and $h(\hat{A})$:  
	\begin{align}
		h(\hat{A})- h(A^{\star})   &\le \bigabs{g(A^{\star}) - h(A^{\star})} + (g(\hat A) - g({A}^{\star})) + \big|g(\hat{A}) - h(\hat{A})\big| \nonumber \\
		&\le \bigabs{g(A^{\star}) - h(A^{\star})}  + \big|g(\hat{A}) - h(\hat{A})\big|\nonumber \\
		&\lesssim n^{-c_\varphi}\cdot n \bignormFro{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 \cdot n \cdot t. \label{eq_g_gap}
	\end{align}
	The second step used the fact that $\hat A$ is the global minimizer of $g(\cdot)$, so that $g(\hat A) \le g({A}^\star)$.
	The third step used equation \eqref{eq_gA_err} and the fact that the spectral norm of $U_A U_A^{\top} - \id_{t\times t}$ is at most one. 
	%With \eqref{eq_g_gap}, we can derive an upper bound on $\bignormFro{A^{\star} {A^{\star}}^{\top}- U_{\hat{A}} U_{\hat{A}}^{\top}}$ as follows. 
	Using equation \eqref{same_hA}, we can verify that
	$$h(\hat A)-h(A^\star) = n \bigtr{{B^\star}^\top\Sigma B^\star ( A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A})} .$$
	Let $\lambda_1\ge\lambda_2 \ge \cdots\ge \lambda_t$ be the eigenvalues of ${B^\star}^\top\Sigma B^\star$.
	Let $v_i$ be the corresponding eigenvector of $\lambda_i$.
	Then, we have $A^\star {A^\star}^\top =\sum_{i=1}^r v_i v_i^\top$, and
	\begin{align}
	h(\hat A)-h(A^\star) = n \sum_{i=1}^r \lambda_i - n\sum_{i=1}^t \lambda_i \| U^\top_{\hat A} v_i\|^2 &= n\sum_{i=1}^r \lambda_i\left(1 -  \| U^\top_{\hat A} v_i\|^2\right)-n\sum_{i=r+1}^t \lambda_i \| U^\top_{\hat A} v_i\|^2 \nonumber\\
	&\ge  n(\lambda_r-\lambda_{r+1}) \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2 , \label{bdd_A-A}
	\end{align}
	where we use $\sum_{i=1}^r \left(1 -  \| U^\top_{\hat A} v_i\|^2\right) = r- \sum_{i=1}^r  \| U^\top_{\hat A} v_i\|^2 =\sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2  $ in the last step.
	On the other hand, we have
	\begin{align*}
	\| A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A}\|_F^2
	&= 2r - 2\inner{A^{\star}{A^{\star}}^{\top}}{U_{\hat{A}} {U_{\hat{A}}}^{\top}} \\
	&= 2 \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2.
	\end{align*}
	Thus from equation \eqref{eq_g_gap} and  \eqref{bdd_A-A}, we obtain that
	$$\| A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A}\|_F^2  =2 \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2 \lesssim \frac{n^{-c_\varphi}\cdot  \bignormFro{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 t}{\lambda_r- \lambda_{r+1}}  .$$
	Hence the proof is complete.
	\end{proof}

@@

	\paragraph{Part 2:} The second part is the cross term, whose expectation over $\cE$ is zero.
	Let $b = B^{\star} \hat{a}_i - \beta^{(i)}$ for simplicity.
	Using Corollary \ref{cor_calE}, the concentration error can be bounded as
	\begin{align*}
		\bigabs{\inner{\Sigma^{1/2}b}{\Sigma^{1/2}R_i}}
		&= \bigabs{\inner{X (X^{\top}X)^{-1} \Sigma b \hat{a}_i^{\top}}{\cE}} \\
		&\le \sum_{j=1}^t \abs{\hat{a}_i(j)} \cdot \bigabs{\inner{X (X^{\top} X)^{-1} \Sigma b}{\varepsilon^{(j)}}} \\
		&\le \sum_{j=1}^t \abs{\hat{a}_i(j)} \cdot n^{\e}\sigma \bignorm{X (X^{\top}X)^{-1} \Sigma b} \\
		&\le \sqrt{t} \norm{\hat{a}_i} \cdot n^{\e} \sigma \bignorm{X (X^{\top} X)^{-1} \Sigma b}.
	\end{align*}
%	\begin{align*}
%		\bigabs{\inner{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)}{\Sigma^{1/2}R_i}} &= \bigabs{\inner{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)}{\cal E}} \\
%		&\le n^{c}\sigma \cdot \bignormFro{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)}\\
%		&\le n^{c}\sigma \cdot\|\hat a_i\| \cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\| \cdot \| (Z^\top Z)^{-1} \|^{1/2} \\
%		&\lesssim n^{-1/2+c}\sigma \cdot\|\hat a_i\| \cdot \bignorm{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)} \\
%		&\le n^{-1/2+c}\sigma^2  \cdot\|\hat a_i\|^2 + n^{-1/2+c} L(B^{\star} \hat{a}_i), 
%	\end{align*}
	In the first step, we plug in the definition of $R_i$ and re-arrange terms.
	In the second step, we use $\hat{a}_i(j)$ to denote the $j$-th coordinate of $\hat{a}_i$.
	In the third step, we use equation \eqref{vcalE}.
	In the last step, we use $\sum_j |\hat a_i(j)|\le \sqrt{t}\|\hat a_i\|$ by Cauchy-Schwarz inequality.
	Finally, we have
	\begin{align*}
		\bignormFro{ X(X^\top X)^{-1}\Sigma b} &=\left[ {b}^\top \Sigma (X^\top X)^{-1}X^\top X(X^\top X)^{-1}\Sigma b \right]^{1/2} \\
		&\le  \|\Sigma^{1/2} b \|  \cdot \left\| \Sigma^{1/2}(X^\top X)^{-1}\Sigma ^{1/2} \right\|^{1/2}  \\
		&=   \|\Sigma^{1/2} b \|  \cdot \left\| (Z^\top Z)^{-1}\right\|^{1/2}  \\
		& \lesssim n^{-1/2} \cdot \norm{\Sigma^{1/2} b}.
	\end{align*}
%	\begin{align*}
%	\bignormFro{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)} &=\|\hat a_i\|\cdot \left[ (B^{\star} \hat{a}_i - \beta_i)^\top \Sigma (X^\top X)^{-1}X^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i) \right]^{1/2} \\
%	&\le \|\hat a_i\|\cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\|  \cdot \left\| \Sigma^{1/2}(X^\top X)^{-1}\Sigma ^{1/2} \right\|^{1/2} \\
%	&= \|\hat a_i\|\cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\|  \cdot \left\| (Z^\top Z)^{-1}\right\|^{1/2}
%	\end{align*}
	Above, we use $X=Z\Sigma^{1/2}$. In the last step, we use Fact \ref{fact_minv}(ii) to bound the operator norm of $Z^\top Z$ by $\OO(n^{-1})$. %, and apply the AM-GM inequality.
	One can see that the concentration error from this part is upper bounded by the result in Claim \ref{claim_pred_err}.

@@

	\paragraph{Part 3:} The final part is the squared term of $R_i$. We rewrite it as
	\begin{align}
	\|\Sigma^{1/2}R_i\|^2 &= \left\|\sum_{j=1}^t \hat{a}_i(j) \Sigma^{1/2}(X^{\top} X)^{-1} X^{\top} \epsilon^{(j)}\right\|^2 \nonumber\\
	& = \sum_{1\le j , k \le t}\hat a_i(j) \hat a_i(k)  {\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} {\epsilon^{(k)}}.\label{E_i^2}
	\end{align}	
%	If $j\ne k$, using Corollary \ref{cor_calE} we obtain that 
%	\begin{align}
%	\left|{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} {\epsilon^{(k)}} \right| &\le \sigma^2 \cdot \bignormFro{X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} } \nonumber\\
%	& =\sigma^2 \cdot \bignormFro{\Sigma^{1/2}(X^{\top} X)^{-1}\Sigma^{1/2}} \nonumber\\
%	&  \le \sigma^2 \cdot p^{1/2} \cdot \bignorm{(Z^{\top} Z)^{-1}} \lesssim \sigma^2 \cdot n^{-1/2+c} \label{jnek}
%	\end{align}
%	with high probability for any small constant $c>0$. On the other hand, if $j=k$, 
	First, for any $1 \le j, k \le t$, the expectation is
	$$\exarg{\cal E}{{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} \epsilon^{(k)}}=\delta_{jk}\cdot \sigma^2\tr\left[\Sigma(X^\top X)^{-1}\right] .$$
	Second, using equation \eqref{vcalA2}, the concentration error is at most
	\begin{align}
	& \left|{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} {\epsilon^{(k)}} -\delta_{jk}\cdot \sigma^2\tr\left[\Sigma(X^\top X)^{-1}\right]\right|\nonumber \\
	\le &n^c\cdot \sigma^2  \bignormFro{X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} } \nonumber \\
	 = & n^c\cdot \sigma^2  \bignormFro{\Sigma^{1/2}(X^{\top} X)^{-1}\Sigma^{1/2}} \nonumber\\
	  \le &\sigma^2 \cdot p^{1/2} \cdot  \bignorm{(Z^{\top} Z)^{-1}}^{1/2} \nonumber\\
	  \lesssim &\sigma^2 \cdot n^{-1/2+c}. \label{jeqk}
	\end{align}
	Above, we used Fact \ref{fact_minv}(ii) in the last step to bound the operator norm of $(Z^{\top} Z)^{-1}$.
	Plugging equation \eqref{jeqk} into equation \eqref{E_i^2}, we obtain that 
	\begin{align*}
		\bigabs{\bignorm{\Sigma^{1/2} R_i}^2 -  \sigma^2 \|\hat a_i\|^2 \cdot\tr\left[\Sigma(X^\top X)^{-1}\right]} \lesssim  \sigma^2 \cdot n^{-1/2+c}  \sum_{1\le j,k\le t}|\hat a_i(j)||\hat a_i(k)| =  n^{-1/2+c} \sigma^2 \cdot  \|\hat a_i\|^2.
	\end{align*}
%	One can verify that the expectation of $\norm{\Sigma^{1/2} E_i}^2$ is equal to $\sigma^2 \norm{\hat{a}_i}^2 \cdot \tr[\Sigma (X^{\top} X)^{-1}]$.
%	Next, we bound the concentration error.
%	Let $A = X (X^{\top} X)^{-1} \Sigma (X^{\top} X)^{-1} X^{\top}$.
%	We have that
%	\begin{align*}
%		\bigabs{\bignorm{\Sigma^{1/2} E_i}^2 - \exarg{\cE}{\bignorm{\Sigma^{1/2} E_i}^2}}
%		&= \bigabs{\inner{A}{\cE \hat{a}_i \hat{a}_i^{\top} \cE^{\top} - \exarg{\cE}{\cE \hat{a}_i \hat{a}_i^{\top} \cE}}}.
%	\end{align*}
%	In the above equation, we note that the trace of $A$ is precisely the trace of $\Sigma (X^{\top} X)^{-1}$.
%	On the other hand, the concentration error of the spectral norm of $\cE \hat{a}_i \hat{a}_i^{\top} \cE^{\top}$ is at most $\sigma^2 \e $.
